### 2016-09-28 intro.tex
cleaning

The concerns outlined above motivate a careful treatment of data
structures in an adversarial setting, where both \emph{soundness}
\jnote{I like soundness better than correctness, but I won't
insist.} and \emph{correctness} are considered. In this work we
initiate such a treatment for abstract data structures, and also
explore the security of several specific data structures---that can
all be viewed as generalizations of Bloom
filters~\cite{bloom1970space}---supporting (approximate)
set-membership queries. Specifically, we show \ldots

>>>>

The concerns outlined above motivate a careful treatment of data
structures in an adversarial setting, where both \emph{soundness}
\jnote{I like soundness better than correctness, but I won't
insist.} and \emph{correctness} are considered. In this work we
initiate such a treatment for abstract data structures, and also
explore the security of several specific data structures---that can
all be viewed as generalizations of Bloom
filters~\cite{bloom1970space}---supporting (approximate)
set-membership queries. Specifically, we show \ldots
\todo{highlight that we are able surface ways in which constructions
  are sensitive to use cases, i.e. schemes secure with secret hash
  functions but not with public hash functions}
\todo{Somewhere in the intro, might what to face the ``nothing hard''
  criticism head on.  Perhaps mention that many of the results follow
  a common pattern (which, for privacy, we tease out in a general
  theorem), and that often the most technically difficult part is
  connnecting the adaptive setting to the zero-query setting.}
